Meeting the Challenges of Modeling Astrophysical Thermonuclear Explosions: \castro, \maestro, and the \amrex\ Astrophysics Suite

### 2017-10-19 astronum_2017/astronum-amrex.tex
add NERSC affil

\author{M. Zingale$^1$,
        A.~S. Almgren$^2$,
        M.~G. Barrios Sazo$^1$,
        V.~E. Beckner$^2$,
        J.~B. Bell$^2$,
        B. Friesen$^2$,
        A.~M. Jacobs$^3$,
        M.~P. Katz$^4$,
        C.~M. Malone$^5$,
        A.~J. Nonaka$^2$,
        D. Willcox$^1$, and
        W. Zhang$^2$}

@@

\address{$^3$Department of Physics and Astronomy, Michigan State
  University, East Lansing, Michigan 48824 USA}

\address{$^4$Nvidia Corporation}

\address{$^5$Los Alamos National Laboratory, Los Alamos, NM, 87545 USA}

>>>>

\author{M. Zingale$^1$,
        A.~S. Almgren$^2$,
        M.~G. Barrios Sazo$^1$,
        V.~E. Beckner$^2$,
        J.~B. Bell$^2$,
        B. Friesen$^3,2$,
        A.~M. Jacobs$^4$,
        M.~P. Katz$^5$,
        C.~M. Malone$^6$,
        A.~J. Nonaka$^2$,
        D. Willcox$^1$, and
        W. Zhang$^2$}

@@

\address{$^3$National Energy Research Scientific Computing Center,
  Lawrence Berkeley National Lab, Berkeley, CA 94720 USA}

\address{$^4$Department of Physics and Astronomy, Michigan State
  University, East Lansing, Michigan 48824 USA}

\address{$^5$Nvidia Corporation}

\address{$^6$Los Alamos National Laboratory, Los Alamos, NM, 87545 USA}
